A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-24 doc/Paper1/ms.tex
Covariance derivations in appendix

Recall that the noise-free light curves of the two images are given by:
\begin{eqnarray}
y_1(t) &=& m_1 + q(t - \tau_1) + \mu_1(t) \\
y_2(t) &=& m_2 + q(t - \tau_2) + \mu_2(t)
\end{eqnarray}
where $\tau_1 = 0$.
Using this, and the model assumptions discussed above, we can obtain the
covariance of $y_1$ with itself at a different time, as well as $y_2$ with itself
at a different time, and $y_1$ and $y_2$ at any time lag.

\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_j(t_2)\right]\\
= \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_j(t_2) - m_j\right)\right]\\
= \mathds{E}\left[\left(q(t_1 - \tau_i) + \mu_i(t_1)\right)
\left(q(t_2 - \tau_j) + \mu_j(t_2)\right)\right]
\end{eqnarray}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\begin{center}
\begin{tabular}{ccc}
Parameter & \vline & Prior \\
\hline
$\tau$ & \vline & $U(-\Delta t/2, \Delta t/2)$ \\ 
$m$ & \vline & $U(y_{\rm min}, y_{\rm max})$ \\
$\sigma_{\rm QSO}$ & \vline & $LU(10^{-3}, 10)$ \\
$L_{\rm QSO}$ & \vline & $LU(10^{-3}\Delta t, 10\Delta t)$ \\
$\sigma_{\rm micro}$ & \vline & $LU(10^{-3}, 10)$ \\
$L_{\rm micro}$ & \vline & $LU(10^{-3}\Delta t, 10\Delta t)$ \\
$\alpha_{\rm micro}$ & \vline & $U(1, 2)$ \\
$\kappa$ & \vline & $LU(1, 10)$
\end{tabular}
\end{center}
\caption{Prior probability distributions for the parameters. $U(a, b)$ denotes
a uniform prior between $a$ and $b$, and $LU(a, b)$ denotes a log-uniform
(that is, uniform in the logarithm of the parameter) prior $\propto 1/x$
between $a$ and $b$. $\Delta t$ is the duration of the data set. All priors
are independent.\label{tab:prior}}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

See the Appendix for derivations.

@@

@@

\appendix
\onecolumn

\section{GP Covariance Function}
Recall that the noise-free light curves of the two images are given by:
\begin{eqnarray}
y_1(t) &=& m_1 + q(t - \tau_1) + \mu_1(t) \\
y_2(t) &=& m_2 + q(t - \tau_2) + \mu_2(t)
\end{eqnarray}
where $\tau_1 = 0$.
Using this, and the model assumptions discussed above, we can obtain the
covariance of $y_1$ with itself at a different time, as well as $y_2$ with itself
at a different time, and $y_1$ and $y_2$ at any time lag. For distinct images
$i$ and $j$ the covariance is:
\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_j(t_2)\right]
&=& \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_j(t_2) - m_j\right)\right]\\
&=& \mathds{E}\left[\left(q(t_1 - \tau_i) + \mu_i(t_1)\right)
\left(q(t_2 - \tau_j) + \mu_j(t_2)\right)\right]\\
&=& \mathds{E}\left[q(t_1 - \tau_i)q(t_2 - \tau_j) + q(t_1 - \tau_i)\mu_j(t_2)
+ \mu_i(t_1)q(t_2 - \tau_j) + \mu_i(t_1)\mu_j(t_2)
\right]\\
&=& S_q\exp
\left[-\frac{|(t_2 -\tau_j)- (t_1-\tau_i)|}{L_q}\right].
\end{eqnarray}
For a single image $i$, the covariance is:
\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_i(t_2)\right]
&=& \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_i(t_2) - m_i\right)\right]\\
&=& \mathds{E}\left[\left(q(t_1 - \tau_i) + \mu_i(t_1)\right)
\left(q(t_2 - \tau_i) + \mu_i(t_2)\right)\right]\\
&=& \mathds{E}\left[q(t_1 - \tau_i)q(t_2 - \tau_i) + q(t_1 - \tau_i)\mu_i(t_2)
+ \mu_i(t_1)q(t_2 - \tau_i) + \mu_i(t_1)\mu_i(t_2)
\right]\\
&=& S_q\exp
\left[-\frac{|(t_2 -\tau_j)- (t_1-\tau_i)|}{L_q}\right] +
S_i\exp\left[
-\left(\frac{|t_2 - t_1|
}{\ell_i}\right)^\alpha
\right]
.
\end{eqnarray}
